\documentclass{tpreiss_cv}

\begin{document}
Tanner Preiss

\email{tanner.preiss@gmail.com}

\cell{484.707.9323}

Objective   To seek a full time position with programming and leadership experience in Security or Software Development.

Availability from January 2015.

\section{Education}
Bachelors of Science - Computer Science: expected December 2014 	                                 08/2011 - present
Minor in Mathematics
Virginia Polytechnic Institute and State University, Blacksburg, VA

\gpa{3.76}{4.00}     			

%--------------------------------------------------------------
\section{Related Experience}

\organization{IBM - Mobile Innovation Lab}{01-2015 - present}
\position{Software Engineer}

TODO: add a description.


\organization{Virginia Tech IT Security Lab (ITSL)}{05/2014-12/2014}
\position{Embedded Systems Security Researcher/Developer}

Implemented dynamic IPv6 address changes in ContikiOS on a Tmote Sky (Internet of Things). Implementation included systems and networking level design(OSI levels 2-7). Published technical paper detailing process and analysis. 

\organization{Virginia Polytechnic Institute and State University - CS Department}{06/2013 - 05/2014}
\position{Undergraduate Teaching Assistant}

Assist students, in CS1054 (Intro to Java), with course work, grade assignments, and supervise programming labs.

\organization{MagnumGroup at Virginia Tech, Blacksburg, VA}{01/2013-05/2013}
\position{Undergraduate Research}

Created regexes and functions to maintain uptime for Android emulators in a large scale Android emulator cloud environment that has capabilities to test and analyze real-world malware.

\organization{A Agency Management, Allentown, PA}{06/2008 - present}
\position{IT Consultant}

Managed and implemented IP security camera systems, Windows Server 2008 servers, ShoreTel IP Phone systems, and OpenVPN solutions. Monitored employee performance via administration tools implemented on    the main server. Recommended solutions for updates, upgrades, and system issues.

%--------------------------------------------------------------
\section{Publications}

%--------------------------------------------------------------
\section{Skills}
\textit{Languages}: C, Java, Python, Scala, HTML (ranked from most proficient >> knowledge of)

\textit{Operating Systems}: Windows, Macintosh, Backtrack (Kali), Ubuntu
Courses(through Fall 2014):    Systems and Networking Capstone, Parallel Computation, Cryptography, Data and Algorithm Analysis, Computer Organization I \& II, Data Structures and Algorithms, Discrete Mathematics

%--------------------------------------------------------------
\section{Other Experience} 
\organization{Cyber Security Club}{08/2011-12/2014}
\position{Member}
Maintain awareness and defense against the daily threats in cyber security, Participate in and practice for security competitions; primarily the Virginia Tech Cyber Security Summit held in the spring.

%--------------------------------------------------------------
\section{Projects}


\textit{MT6D (Moving Target IPv6 Defense)}

Implemented dynamic IPv6 address changing, on an embedded, Internet of Things, device in ContikiOS. The implementation required knowledge of protocols such as IPv6, 6LoWPAN, RPL, ICMPv6, Rime Stack, uIP stack.

\textit{BinTree with Memory Manager and LRU Buffer Pool} (Java)

Implemented a BinTree, a modified PR-Quad Tree, with variable length records. A memory manager was used to decide where in the file to store BinTree nodes and records. The memory manager used both a free list with circular first fit algorithm and a buffer pool with least recently used (LRU) algorithm to mediate the disk accesses.

%--------------------------------------------------------------
\section{Awards}
Deans List Fall 2013, Spring 2014                  
Virginia Tech Cyber Security Summit 2013 (1st Place Team), 2014 (1st Place Team)

\section{Extended Links/Interests}

Internet : www.github.com/t-preiss  :  www.youtube.com/tntmodzinc  (1000+ subscribers, 500k views) :







\end{document}